MSCA 31006: Final Project - AQI Forecasting

### 2023-08-14 MSCA_31006_Time_Series_Final_Project.Rmd
Add files via upload

>>>>

#### Step 9a: Forecast using ETS - Weekly

```{r, tidy=TRUE}
# Build the exponential smoothing model
model_ets_weekly <- ets(train_weekly, lambda="auto", additive.only=TRUE)
summary(model_ets_weekly)
forecast_ets_weekly <- forecast(model_ets_weekly, h=110)

# Plot the forecasts for ETS model
plot(forecast_ets_weekly, main = "PM 2.5 AQI Forecast - ETS",
         xlab = "Month", ylab = "PM 2.5 AQI")
lines(test_weekly)

# Compare the forecast with the actual test data by calculating MAPE and MSE
# Mean Absolute Percentage Error (MAPE)
mape_ets_weekly <- mean(abs((test_weekly - forecast_ets_weekly$mean)/test_weekly))
mape_ets_weekly

# Mean Absolute Error (MAE)
mae_ets_weekly <- mean(abs((test_weekly - forecast_ets_weekly$mean)))
mae_ets_weekly

# Mean Squared Error (MSE)
mse_ets_weekly <- mean((test_weekly - forecast_ets_weekly$mean)^2)
mse_ets_weekly

# Evaluate the residuals
checkresiduals(forecast_ets_weekly)

Box.test(residuals(forecast_ets_weekly), lag = 52, type = "Ljung-Box")
